(Working Title) Properties of the \KT\ Campaign 1 Planets, False Positive Probabilities, and Confirmation of $N$ Systems. You Were Warned: it's a Working Title.

### 2015-02-26 ms.tex
text tweaks

@@

\begin{abstract}
\btmtodo{This is where the abstract will go}
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a \btmtodo{Radius} planet with $T_{eq} = $\btmtodo{Temp} and an 
orbital period of 33 days.
\end{abstract}

@@

>>>>

\newcommand{\paperip}{\citep{Foreman-Mackey15}}
\newcommand{\paperit}{\citet{Foreman-Mackey15}}

@@

\begin{abstract}
\btmtodo{This is where the abstract will go}
Of the 36 planet candidates presented in \paperit{} we confirm 
\btmtodo{Nconfirm} as planets and \btmtodo{NFP} as false positives
at the \btmtodo{confidence} level. Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a \btmtodo{Radius} planet with $T_{eq} = $\btmtodo{Temp} and an 
orbital period of 33 days.
\end{abstract}

@@

\section{Planet Properties}

This is Dan?
